### 2017-09-10 paper/evaluation.tex
Fixed mispelling (ElectricTest, not TestElectric)

\sloppy Table~\ref{tab:rq6-table} summarizes results ordered by
subject's name.  Values are averaged across multiple executions.  We
did not report standard deviations as they are very small in all
cases.  As to identify the potential causes of flakiness, we inspected
the exceptions reported in execution logs. We found that, in most
of the cases, flakiness was caused by race conditions: approximately
97.5\% of the failures were caused by a \CodeInF{null} dereference and 1.6\% were
caused by concurrent access on unsynchronized data structures.\Comment{
  More precisely, the manifested exceptions were
  \CodeInF{ConcurrentModificationException} (0.8\%),
  \CodeInF{NoSuchElementException} (0.7\%), and
  \CodeInF{ArrayIndexOutOfBoundsException} (0.7\%).}  Cases of likely
broken test dependencies were not as prevalent as race conditions
(0.8\% of the total): \CodeInF{EOFException} (0.2\%),
\CodeInF{FileSystemAlreadyExistsException} (0.2\%), and
\CodeInF{BufferOverflowException} (0.4\%). Results suggest that
anticipating race conditions to schedule test executions would have
higher impact compared to breaking test dependencies using a tool such
as TestElectric~\cite{bell-etal-esecfse2015}.

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile FC
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs dir
%%  LocalWords:  xml basicstyle boxpos numberstyle deletekeywords JVM
%%  LocalWords:  uncompilable leftmargin quartile DskipTests forkMode
%%  LocalWords:  threadCount forkCount lrr BounceStorage Flink Gerrit
%%  LocalWords:  JenkinsCI Spotify Javaslang Jcabi Github Hazelcast
%%  LocalWords:  Jankotek MapDB Dparallel classesAndMethods Mapstruct
%%  LocalWords:  DataflowJavaSDK modularized JUnit llrrr lightgray rr
%%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock io
%%  LocalWords:  mapdb workflow XPath boxplot llcr javaslang jcabi
%%  LocalWords:  github hazelcast jankotek OpenNLP yegor Rultor vavr
%%  LocalWords:  Vavr SNE Urbanairship Datacube dereference
%%  LocalWords:  unsynchronized ConcurrentModificationException
%%  LocalWords:  NoSuchElementException EOFException TestElectric
%%  LocalWords:  ArrayIndexOutOfBoundsException
%%  LocalWords:  FileSystemAlreadyExistsException
%%  LocalWords:  BufferOverflowException

>>>>

\sloppy Table~\ref{tab:rq6-table} summarizes results ordered by
subject's name.  Values are averaged across multiple executions.  We
did not report standard deviations as they are very small in all
cases.  As to identify the potential causes of flakiness, we inspected
the exceptions reported in execution logs. We found that, in most
of the cases, flakiness was caused by race conditions: approximately
97.5\% of the failures were caused by a \CodeInF{null} dereference and 1.6\% were
caused by concurrent access on unsynchronized data structures.\Comment{
  More precisely, the manifested exceptions were
  \CodeInF{ConcurrentModificationException} (0.8\%),
  \CodeInF{NoSuchElementException} (0.7\%), and
  \CodeInF{ArrayIndexOutOfBoundsException} (0.7\%).}  Cases of likely
broken test dependencies were not as prevalent as race conditions
(0.8\% of the total): \CodeInF{EOFException} (0.2\%),
\CodeInF{FileSystemAlreadyExistsException} (0.2\%), and
\CodeInF{BufferOverflowException} (0.4\%). Results suggest that
anticipating race conditions to schedule test executions would have
higher impact compared to breaking test dependencies using a tool such
as ElectricTest~\cite{bell-etal-esecfse2015}.

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile FC
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs dir
%%  LocalWords:  xml basicstyle boxpos numberstyle deletekeywords JVM
%%  LocalWords:  uncompilable leftmargin quartile DskipTests forkMode
%%  LocalWords:  threadCount forkCount lrr BounceStorage Flink Gerrit
%%  LocalWords:  JenkinsCI Spotify Javaslang Jcabi Github Hazelcast
%%  LocalWords:  Jankotek MapDB Dparallel classesAndMethods Mapstruct
%%  LocalWords:  DataflowJavaSDK modularized JUnit llrrr lightgray rr
%%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock io
%%  LocalWords:  mapdb workflow XPath boxplot llcr javaslang jcabi
%%  LocalWords:  github hazelcast jankotek OpenNLP yegor Rultor vavr
%%  LocalWords:  Vavr SNE Urbanairship Datacube dereference
%%  LocalWords:  unsynchronized ConcurrentModificationException
%%  LocalWords:  NoSuchElementException EOFException ElectricTest
%%  LocalWords:  ArrayIndexOutOfBoundsException
%%  LocalWords:  FileSystemAlreadyExistsException
%%  LocalWords:  BufferOverflowException
